---
title: "Analysis"
output: html_document
date: "2023-02-15"
---

Part I: 

Import the Sequences.csv file.

```{r}
data<-read.csv("Sequences.csv")
str(data)
head(data)
```

Count the number of each base pair (A, T, C and G), in each of the three sequences. (Hint: do not include any characters from the header, use the nucleotide sequence only; you MIGHT use gsub(), nchar(), for loops, if/then statements). Print out each sequence. Print out the number of each nucleotide as a table for each of the three sequences.

```{r}
  A_count <- nchar(gsub("[^A]", "", data))
  T_count <- nchar(gsub("[^T]", "", data))
  C_count <- nchar(gsub("[^C]", "", data))
  G_count <- nchar(gsub("[^G]", "", data))
  
cat("Sequence:", seq, "\n")
  cat("A count:", A_count, "\n")
  cat("T count:", T_count, "\n")
  cat("C count:", C_count, "\n")
  cat("G count:", G_count, "\n\n")
```

Include an image of a bacteria from the internet, and a link to the Wikipedia page about Borrelia burgdorferi



Calculate GC Content (% of nucleotides that are G or C) and create a final table showing GC content for each sequence ID

```{r}
calculate_gc <- function(data) {
  gc_count <- sum(strsplit(data, "")[[1]] %in% c("G", "C"))
  gc_content <- gc_count / nchar(data) * 100
  return(gc_content)
}

# Apply the function to each sequence in the data frame and create a new column for GC content
data$GC_content <- sapply(data$Sequence, calculate_gc)

# Print the final table with sequence IDs and their corresponding GC content
print(data)

```

Part II: 

```{r}

library(rentrez)
library(ggplot2)

# Search parameters
search_terms <- "human [Organism] AND mitochondrion [filter]"
db <- "nucleotide"
retmax <- 1

# Search GenBank
search <- entrez_search(db, term = search_terms, retmax = retmax)
id <- search$ids
seq <- entrez_fetch(db, id = id, rettype = "fasta")

# Print retrieved sequence
cat("Query sequence:\n", seq, "\n")

# Align sequences
aln <- AlignSeqs(Seqs = seq, searchDB = "nt", n = 5, verbose = FALSE)

# Plot similarity scores
sim_scores <- ScoreSimilarity(aln)
sim_scores_df <- as.data.frame(sim_scores)
ggplot(sim_scores_df, aes(x = Sequence, y = Score)) +
  geom_col(fill = "steelblue") +
  theme_minimal() +
  xlab("Sequence") +
  ylab("Similarity Score") +
  ggtitle("Sequence Similarity Scores")
```






